### 2016-04-18 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
DSR edits

Fig2A <- ggplot(temp,aes(x = LayYear,y = RTL))+
  ylab('RTL') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top')+
  geom_jitter(col = 'grey')+
  geom_boxplot(outlier.colour = NA,notch=F,alpha=0.2)+
  scale_colour_manual(values = c('grey','darkorange'))+
  scale_fill_manual(values = c('grey','darkorange'))+
  annotate('text',x = 1,y = 2.1,label = 'A')

temp$LayYear <- as.numeric(paste(temp$LayYear))

Fig2B <- ggplot(temp,aes(x = LayYear,y = Density))+
  ylab('Adult population size') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none')+
  geom_line(stat = 'identity')+
  annotate('text',x = 1998,y = 360,label = 'B')

pdf('Figures/Figure 2.pdf',
    width = 8,
    height = 6,
    paper = 'a4r')
multiplot(Fig2A,Fig2B,layout=matrix(c(1,2),nrow = 2,byrow=T))
dev.off()

@@

#Run the model
lm2 <- lmer(RTL ~ Agemonths*(Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ)  + (1|FieldPeriodID) + (1|TerritoryID)+(1|PlateID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

@@

Fig3A <- forestplot(table2)+
  annotate('text',x = 1,y = 0.25,label = 'A')

@@

temp <- Loss
#Run the model
lm2 <- lmer(Loss ~ Agemonths*(Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ) + (1|FieldPeriodID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

@@

@@

Fig5B <- ggplot(temp,
       aes(x = `Age (months)`,
           y = Loss,
           fill=Helpers)) +
  theme_classic() +
  ylab(expression(Delta*'RTL'))+
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_jitter(aes(colour = Helpers),position=position_jitterdodge(dodge.width = 0.8))+
  geom_boxplot(outlier.colour = NA,notch=F,alpha=0.2)+
  scale_colour_manual(values = c('grey','darkorange'))+
  scale_fill_manual(values = c('grey','darkorange'))+
  geom_abline(slope = 0,intercept = 0,lty = 2)+
  annotate('text',x = 0.55,y = 1.5,label = 'C')

pdf('Figures/Figure 5.pdf',
    width = 8,
    height = 8,
    paper = 'a4')
multiplot(Fig5A,Fig5B)
dev.off()

>>>>

Fig2 <- ggplot(temp,aes(x = LayYear,y = RTL))+
  ylab('RTL') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top')+
  geom_jitter(col = 'grey')+
  geom_boxplot(outlier.colour = NA,notch=F,alpha=0.2)+
  scale_colour_manual(values = c('grey','darkorange'))+
  scale_fill_manual(values = c('grey','darkorange'))

pdf('Figures/Figure 2.pdf',
    width = 8,
    height = 4,
    paper = 'a4r')
Fig2
dev.off()

@@

#Run the model
lm2 <- lmer(RTL ~ Agemonths*(Tarsus) + Helper + NonHelper + Sex + BodyMass  + TQ  + (1|FieldPeriodID) + (1|TerritoryID)+(1|PlateID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

@@

Fig3A <- forestplot(table2)+
  annotate('text',x = 0.8,y = 0.25,label = 'A')

@@

temp <- Loss
#Run the model
lm2 <- lmer(Loss ~ TimeDiff+Agemonths*Helper+Tarsus + NonHelper + Sex + BodyMass  + TQ + (1|FieldPeriodID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

@@

table2 <- data.frame(table2,myx=row.names(table2))
table2 <- table2[rownames(table2) != 'z.TimeDiff',]
table2$myx <- factor(table2$myx,levels = table2$myx[order(table2$Estimate,decreasing = T)])

@@

Fig5B <- ggplot(temp,
       aes(x = `Age (months)`,
           y = Loss,
           fill=Helpers)) +
  theme_classic() +
  ylab(expression(Delta*'RTL'))+
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_jitter(aes(colour = Helpers),position=position_jitterdodge(dodge.width = 0.8))+
  geom_boxplot(outlier.colour = NA,notch=F,alpha=0.2)+
  scale_colour_manual(values = c('grey','darkorange'))+
  scale_fill_manual(values = c('grey','darkorange'))+
  geom_abline(slope = 0,intercept = 0,lty = 2)+
  annotate('text',x = 0.55,y = 1.5,label = 'B')

Fig5C <- ggplot(temp,
       aes(col = `Age (months)`,
           fill =  `Age (months)`,
           y = Loss,
           x=TQ)) +
    ylab(expression(Delta*'RTL'))+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point()+
  stat_smooth(method = 'lm')+
  scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 3,y = 1.3,label = 'C')

pdf('Figures/Figure 5.pdf',
    width = 8,
    height = 8,
    paper = 'a4')
multiplot(Fig5A,Fig5B,Fig5C,layout = matrix(c(1,1,2,3),nrow=2,byrow = T))
dev.off()
